Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

  The probability distribution of a protocol $\prog$ (as a pmf) can be precisely computed
  by interpretation as a \cemph{constraint program}.
  \begin{itemize}
  \item Interpretation as a Datalog program-- set of Least Herbrand Models.
    \begin{itemize}
      \item Random tapes represented as fact base.
    \end{itemize}
  \item Interpretation as SMT constraints\footnote{Ozdemir, A., Kremer, G., Tinelli, C., Barrett, C. (2023). \emph{Satisfiability Modulo Finite Fields}. In: Enea, C., Lal, A. (eds) Computer Aided Verification. CAV 2023. }-- set of all models.
  \end{itemize}
  Set of models can be queried to enforce hyperproperties-- but poor scaling.

>>>>

  The probability distribution of a protocol $\prog$ (as a pmf) can be precisely computed
  by interpretation as a \cemph{constraint program}.
  \begin{itemize}
  \item $\mathbb{F}_2$ interpretation as a Datalog program-- set of Least Herbrand Models.
    \begin{itemize}
      \item Random tapes represented as fact base.
    \end{itemize}
  \item $\mathbb{F}_p$ interpretation as SMT constraints\footnote{Ozdemir, A., Kremer, G., Tinelli, C., Barrett, C. (2023). \emph{Satisfiability Modulo Finite Fields}. In: Enea, C., Lal, A. (eds) Computer Aided Verification. CAV 2023. }-- set of all models.
  \end{itemize}
  Set of models can be queried to enforce hyperproperties-- but poor scaling.
